---
title: "Conferences/ Talks"
output: 
  html_document:
  code_folding: hide
---
<br> <br>

## ISVEE 2024
### Sydney, Australia
Oral presentation

<details>
```{r, echo = F}
  htmltools::includeMarkdown('./talks/24-isvee24.md')
```
</details><br><br>

## EEID 2024
### Stanford, CA, USA
Poster presentation

<details>
```{r, echo = F}
  htmltools::includeMarkdown('./talks/24-eeid24.md')
```
</details><br><br>

## UCDavis Postdoc Symposium 2024
### Davis, CA, USA
Oral presentation

<details>
```{r, echo = F}
  htmltools::includeMarkdown('./talks/24-ucdpdsym2024.md')
```
</details><br><br>

## ISESSAH 2023
### Helsinki, Finland
Oral presentation

<details>
```{r, echo = F}
  htmltools::includeMarkdown('./talks/23-isessah23.md')
```
</details><br><br>

## VEEC 2022
### Wageningen, Netherlands
Oral presentation

<details>
```{r, echo = F}
  htmltools::includeMarkdown('./talks/22-veec22.md')
```
</details><br><br>

## ISVEE 2022
### Halifax, Canada
Oral presentation

<details>
```{r, echo = F}
  htmltools::includeMarkdown('./talks/22-isvee16.md')
```
</details><br><br>

## ISESSAH 2022
### Halifax, Canada
Poster presentation

<details>
```{r, echo = F}
  htmltools::includeMarkdown('./talks/22-isessah22.md')
```
</details><br><br>

## SVEPM 2021
### Tolouse/ Online
Oral presentation

<details>
```{r, echo = F}
  htmltools::includeMarkdown('./talks/21-svepm21.md')
```
</details><br><br>